### 2017-05-22 PAPER/a_Thesis/Masterarbeit.tex
add paper and code for C' and L'

% Alter some LaTeX defaults for better treatment of figures:
% See p.105 of "TeX Unbound" for suggested values.
% See pp. 199-200 of Lamport's "LaTeX" book for details.
%   General parameters, for ALL pages:
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

@@

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Quantum cascade lasers (QCLs) are compact, electrically pumped semiconductor devices, which are considered to be promising light source for mid-infrared and terahertz radiation. Benefit from this special mechanism they can utilize the electric power more efficiently than other diode lasers and achieve a high output power. Despite its practical significance, generating ultra short pulses from QCLs by mode-locking has achieved only limited success in the past decade. In this work, we study the influence of external source on the mode-locking of QCLs. A dynamic model based on Maxwell-Bloch equations as well as transmission line was build to simulate QCLs in time domain. The simulation results were then analyzed and compared with existing experiment results from references to check reliability of the established model.

The purpose of this research is to build a new model based on existed simulation methods to achieve a dynamic modeling of QCLs in time domain, which would help to get a better understanding of its theoretical mechanism and redound to search for optimal parameters of mode-locking in experiments.

\chapter*{Acknowledgements} 
\addcontentsline{toc}{chapter}{Acknowledgements}

Thanks to Petar

@@

\chapter*{List of Symbols}

% ============================
%  Content
% ============================

\tableofcontents

\chapter{Introduction}\pagenumbering{arabic}
The operating principle of QCLs was first proposed by R.F. Kazarinov and R.A. Suris in 1971 \cite{kazarinov1971possibility}. However, due to the complexity of fabrication process until 1994 QCLs was firstly demonstrated at Bell Laboratories by Jerome Faist and his colleagues \cite{faist1994quantum}. They have gained considerable attention afterwards. Unlike common semiconductor lasers, which utilize electron-hole recombination to realize electromagnetic radiation, QCLs are unipolar and their emission is based on intersub- band transitions in coupled quantum well superlattices \cite{williams2007terahertz}. Due to lack of suitable radiation sources and detectors this region remains one of the least developed spectral regions. The occurance of QCLs provides a option as a prominent source to help investigate these regions, because their emission wave length as well gain spectrum can be engineered through various design \cite{gmachl2002ultra}. To date, only n-type QCLs are successfully realized lasing.  One of the most commonly used material combination for active region is GaAs (well) and $Al_{x}Ga_{1-x}As$ (barrier), where x is the relative amount ration of aluminum to gallium. The intersubband transmission occurs in conduction band, as Fig. shows. Add--> one module of repeated QCL heterostructures!

As a novel type of laser as well as efficient source to generate THz radiation, THz QCLs showed great potential and have attracted already a lot attentions for developing their possible applications. Compared to X-ray, THz radiation has lower energy ($E=h\nu$), but still can penetrate many materials (e.g. clothes, paper) except for metals. Therefore, it could be used as imaging and sensing for security detection in airport \cite{federici2005thz}, which wouldn't affect the health of our bodies. Another interesting area is astronomy, such as heterodyne receivers \cite{williams2007terahertz}, which requires THz QCLs. Because the radiation from universe is mainly with THz, the research of THz technologies would help to detect and observe those unnoticed radiation from galaxies.

@@

Although there are already those successful experimental attempts by active mode-locking, but a complete theory system is still not available. Due to limited knowledge of unfavorable physical effects and lack of consolidation theory about its mechanism, it has been proven to be difficult to directly employ existing techniques from the ultra fast optics community to realize mode-locking of QCLs.

\section{Related work}
Accompanied with experimental research, modeling techniques for QCLs are also steady investigated to help get a deep understanding of internal mechanisms and explore unknown effects. Thanks for persistent efforts of researchers, there are already several models as well as solvers which could be used for describing and analyzing various of processes in QCLs, such as density matrix approach, Maxwell-Bloch equations, non-equilibrium Green’s function theory along with some other modified methods aimed to take more linearities and effects into account. These models have been used, for example, to investigate modulation properties of optical injection-locked QCLs \cite{wang2013rate}, to calculaton for four-level scheme THz QCLs \cite{yasuda2009nonequilibrium}.

@@

\section{Objective}
The objectives of this thesis are as follows:

1). To build a new dynamic model based on Transmission line

2). To verify "pulling effect" in mode-locking through simulation

3). To acquire optimal simulation parameters to generate short pulse

4). To gain a deep understanding of mode-locking behaviors to obtain a better design in the future.

\chapter{Theory}
QCL is composed of a great amount of repeated stacks of heterojunctions, its extreme thin layers (in the order of a few nanometers) of different materials result in the formation of quantum wells and barriers. By solving steady Schroedinger-Poisson equation system, eigenenergies and wave functions of eigenenergies can be determined, which help to engineer and optimize QCLs (e.g. radiation frequency, injection efficiency).  Transfer matrix method \cite{jonsson1990solving} and finite-difference method \cite{tan1990self} are widely used to compute the numerical solution of the system efficiently. 
\section{Maxwell-Bloch equations}
To describe carrier dynamics as well as light propagation in a laser, Maxwell-Bloch equations can be used as a empirical approach. 
****-->Introduction of FL183S
Maxwell's equations-->explaination of the equation

Bloch equations-->3 levels for example

\section{Transmission line}
Transmission line model was created by Oliver Heaviside \cite{heaviside2008electromagnetic} and usually consists of two separated conductors and medium in between (Fig. \ref{fig:TLcircuit}). The conventional TLM is based on Telegrapher's equations (\ref{eq:TLequation1})(\ref{eq:TLequation2}), which describe the evolution of voltage and current both spacial and temporal on an electrical transmission line. These two differential equations contains four distributed components (R', L', G', C') which vary from different transmission lines: R' is distributed resistance of conductors, which is represented by a series resistor in ohms per unit length ($\Omega /m$); L' is distributed inductance resulting from the magnetic field around the line due to self-inductance, which is represented by a series inductor in henries per unit length ($H/m$); G' is distributed conductance of the dielectric material separating the two conductors, which is expressed in siemens per unit length ($S/m$) and represented by a shunt resistor with resistance of 1/G'; C' is distributed capacitance of transmission line, which is represented by a shunt conductor in farads per unit length ($F/m$).

Transmission line can be further classified in lossy/non-lossy transmission line and uniform/nonuniform transmission line with regarding to characteristics of its conductors and medium. When no resistance (idea conductor) and conductance (idea dielectric medium) exist, it can be regarded as ideal transmission line which contains only L' and G'. In uniform transmission line all those distributed components are uniformly distributed along line. Therefore, under the assumptions above the simulated QCL can be defined as a 1D nonlinear lossy transmission line.

% TL equivalent circuit figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{images/TLcircuit}
\caption{: An equivalent circuit representation of a differential section of the waveguide with capacitance per unit length C’ and inductance per unit length L’.}
\label{fig:TLcircuit}
\end{center}
\end{figure}
% Transmission line equations
Telegrapher's equations:
\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation1}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-G'v(x,t) \label{eq:TLequation2}
\end{eqnarray}

\section{Mode-locking}
Light generated by lasers owns high coherent compared with from other light sources. Nevertheless, it has still large bandwidth of optical gain, the modes inside cavity osculate independently and don't have fix phase, which leads to wide pulse. By uncertainty principle, if pulse duration is quite short, its bandwidth muss be larger. For example, a hyperbolic-secant-squared pulse shape is often assumed for lasers generating ultrashort pulse, the minimum possible pulse duration $\Delta t$ can be calculated with
\begin{equation}
\Delta t=\frac{0.315}{N\Delta \nu}.
\end{equation}
Where 0.315  is pulse shape dependent time bandwidth product, which for Gaussian shape pulse is 0.441. N and $\Delta \nu$ is amount of modes and bandwidth of pulse, respectively. This formula above could be be used for roughly evaluating the shortest possible pulse width. However, in real case, many other factors have to be taken into consideration, such as dispersion of the cavity, pulse shape and so on.

@@

fundamentals of mode-locking knowledge: FP, locking range, modes.....
Ideally it is exactly at $ f_{tr}$, but even if modulated at frequency of a little variation with $ f_{tr}$, the laser could still be mode-locked, the maximal possible frequency interval is called locking range.
\chapter{Model}
The dynamic model consists of two parts. One of them is optical modeling, which is used for describing the carrier transport  as well as light propagation inside cavity (microcosmic). The other is based on transmission line to obtain voltage and current distribution along cavity (microcosmic). Although each of them has separate solver, both will be simulated simultaneously and can affect with each other.
\section{Optical modeling}
Similar with the existing modeling methods, in this model light propagation is described with Maxwell' equation while carrier transportation is determined by Bloch equation. Without regard to lateral non-uniform distribution at boundaries \cite{huang2014non, dhar2015nanoscopic} QCL can be simplified to one-dimensional (1D) structure in the direction of propagation (x axis), which means the electrical components were uniformly distributed throughout the cross-sectional area.

\subsection{Carrier transport}
To simulate QCL active regions, we adapt the density matrix model from Ref. [cite Belyanin], to include total of four subband levels, and more importantly to allow all relevant system parameters, such as the eigenenergies, dipole moments and all scattering rates to be bias dependent.

As a prototypical QCL design, we take the sub-band structure configuration illustrated in Fig. \ref{fig:4Levels}, consisting of 4 relevant levels per period, i.e. levels from 1 to 4, where level 4 denotes the upper laser state, level 3 the lower laser level, level 2 is an extraction level which eases the electron extraction from 3, and finally level 1 denotes the depopulation level of the period, which also coincides with the injector state (1') of the next module. Typical QCL designs consist of more than 30 repetitions of this schematic, however we can employ periodic boundary conditions [cite] and restrict our attention to a single period only.

@@

The time evolution of the density matrix is given by the von Neumann equation, which we couple to a wave equation for $E_z(x,t)$, denoting the $z$-component electric field (and also the assumed laser growth direction).  
\begin{subequations}
	\label{eq:dmequations}
 \begin{align}
	\frac{d\rho_{44}}{dt} &= J +i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 4} \frac{\rho_{jj}}{\tau_{j\rightarrow 4}}  - \frac{\rho_{44}}{\tau_{4}}, \\
	\frac{d\rho_{33}}{dt} &= -i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 3} \frac{\rho_{jj}}{\tau_{j\rightarrow 3}} - \frac{\rho_{33}}{\tau_{3}}, \\
	\frac{d\rho_{22}}{dt} &= \sum_{j\neq 2} \frac{\rho_{jj}}{\tau_{j\rightarrow 2}} - \frac{\rho_{22}}{\tau_{2}}, \\
	\frac{d\rho_{11}}{dt} &=  -J + \sum_{j\neq 1} \frac{\rho_{jj}}{\tau_{j\rightarrow 1}} - \frac{\rho_{11}}{\tau_{1}}, \\
	\frac{d\rho_{43}}{dt} &= - i\omega_{43}\rho_{43} + i\frac{ez_{43}}{\hbar}E_z(\rho_{44}-\rho_{33})-\Gamma_{\parallel 43}\rho_{43}.
 \end{align}
\end{subequations}
In Eqs. (\ref{eq:dmequations}) $\rho_{ij}$ denotes the $ij-$th density matrix element,  $z_{43}$ the optical transition's dipole moment, $e$ the elementary charge, $\hbar$ is the reduced Plank's constant. Also the parameter $1/\tau_{i\rightarrow j}$ is the net scattering rate from level $i$ to level $j$, calculated by our ensemble Monte Carlo code and incorporating, amongst others, longitudinal optical (LO) phonon, interface roughness and electron electron scattering mechanisms [cite]. Lastly $1/\tau_{i} = \sum_j 1/\tau_{i\rightarrow j}$ is the inverse lifetime of level $i$ and $\Gamma_{\parallel 43} = (\tau_4+\tau_3)/(2\tau_4\tau_3)+1/\tau^*$ is the dephasing rate of the optical transition, including lifetime broadening and a phenomenological pure dephasing $1/\tau^*$ rate due to intrasubband scattering processes [cite ANDO model]. The only scattering mechanism treated quantum mechanically is the optical transition between the upper and lower laser states. One can also fully coherently include resonant tunneling between the injector 1' and the upper laser state 4, which leads to a modified system of equations with larger number of independent variables and is thus more computationally demanding [cite]. Furthermore such an approach does not allow for the inclusion (without $k-$space discretization) of second order tunneling current into the simulations, which has been shown to be the origin of negative the differential conductivity and dispersive gain  in quantum cascade lasers []. This is why in this publication we adhere to the more intuitive model from [cite Belyanin], which can be easily adapted to include various models for the current density via the term $J$ in the above equations. Keeping in foresight that we would like to couple the density matrix equations to an electrical model for the waveguide, we find the later model as the more suitable alternative.

@@

\subsection{Light propagation}
****-->rewrite, give more explanation for concept polarization P

In order to include the electric field dynamics into the overall picture, we write down the inhomogeneous wave equation 
\begin{align}
\label{eq:waveqn}
\left [\frac{c^2}{n_{THz}^2} \frac{\p^2}{\p x^2} -\frac{\p^2}{\p t^2} \right ] E_z =\frac{1}{\epsilon_0 n_{THz}^2}\frac{\p^2}{\p t^2}P,
\end{align}
where  $n_{THz}$ denotes the background refractive index of the bulk active region, $c$ is the velocity of light in vacuum and $\epsilon_0$ is the permittivity of free space. The symbol $P$ denotes the (nonlinear) polarization of the two level system and is given by 
\begin{equation}
P(x,t) =  -\frac{n^s}{L_p}\Gamma ez_{43} (\rho_{43}+\rho_{34}),  
\end{equation}
with $\Gamma$ is the field confinement factor and $L_p$ is the period length.

For the final set of equations, we also employ the rotating wave and slowly varying envelope approximations [cite], which allows us to reduce  the wave equation (\ref{eq:waveqn}) to a pair of propagation equations, an also eliminate fast oscillating terms from the density matrix equations (\ref{eq:dmequations}). The corresponding final formulas are slightly modified versions of those in [cite me, cite belyanin], and therefore we omit them here for brevity. We would like to point out also that in all subsequent calculations, we have also taken into consideration the effect of the inversion grating on to the current density, in an analogous manner to [cite belyanin].

@@

\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation5}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-wJ'(x,t). \label{eq:TLequation6}
\end{eqnarray}
where, v(x,t) and i(x,t) are voltage and current signal at a node
\subsubsection{Boundary conditions}
Boundary conditions account for the completeness of differential equations at the boundary. In order to refine the boudaries and avoid hard variation of electrical components, a cascading of $\pi$ networks\cite{orlandi1996fdtd} is introduced for the distributed transmission line by splitting the shunt capacitance and conductance in half with two parallel capacitors and conductors at boundary, which is illustrate in Fig. \ref{fig:BoundaryCondition}.

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltaged can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. As the right side of QCL lefts open, no current component exists at the end node. Consequently, the boundary condition for current is definitely ${I}_{end}^{n} = 0$. Besides, due to existance of wire impedance (50 $\Omega$) there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.55]{images/pi_representation}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit. Error: $I_{N-\frac{1}{2}}$}
\label{fig:BoundaryCondition}
\end{center}
\end{figure}

>>>>

% Alter some LaTeX defaults for better treatment of figures:
% See p.105 of "TeX Unbound" for suggested values.
% See pp. 199-200 of Lamport's "LaTeX" book for details.
%   General parameters, for ALL pages:
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages
\renewcommand{\labelenumi}{\roman{enumi})}

@@

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Quantum cascade lasers (QCLs) are compact, electrically pumped semiconductor devices, which are considered to be promising light source for mid-infrared and terahertz radiation. Benefit from this special mechanism they can utilize the electric power more efficiently than other diode lasers and achieve a high output power. Despite its practical significance, generating ultra short pulses from QCLs by mode-locking has achieved only limited success in the past decade. In this work, we studied the influence of external source on the mode-locking of QCLs. A dynamic model based on Maxwell-Bloch equations and transmission line was build to simulate QCLs in time domain. The simulation results were then analyzed and compared with existing experiment results from references to check reliability of the established model.

The purpose of this research is to combine the existing simulation methods and transmission line to build a new model for dynamic modeling of QCLs, which would help to get a better understanding of its theoretical mechanism and redound to search for optimal parameters of mode-locking in experiments.

\chapter*{Acknowledgements} 
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to express my deep gratitude to my supervisor Prof. Christian Jirauschek and Mr. Petar Tzenov for their support and constructed criticism during my master thesis project. Especially for Petar, from advance seminar to master thesis, he behaved always modest, professional and patient in my mind. I thank him for being my mentor and friend.

I would like to thank Assistant Professorship of Computational Photonics of TUM, which provides a friendly atmosphere and the opportunity to carry on a research in QCL area. I also want to thank other members in this group Mr. Mark Schmidt and Mr. Michael Riesch. Although we focus on different topics, we had lots of inspiring discussions and I learned a lot from them.

@@

%\chapter*{List of Symbols}
%
%
%% ============================
%%  Content
%% ============================
%
%\tableofcontents

\chapter{Introduction}\pagenumbering{arabic}
The operating principle of QCLs was first proposed by R.F. Kazarinov and R.A. Suris in 1971 \cite{kazarinov1971possibility}. However, due to the complexity of fabrication process until 1994 QCLs was firstly demonstrated at Bell Laboratories by Jerome Faist and his colleagues \cite{faist1994quantum}. They have gained considerable attention afterwards. Unlike common semiconductor lasers, which utilize electron-hole recombination to realize electromagnetic radiation, QCLs are unipolar and their emission is based on intersub- band transitions in coupled quantum well superlattices \cite{williams2007terahertz}. Due to lack of suitable radiation sources and detectors this region remains one of the least developed spectral regions. The occurance of QCLs provides a option as a prominent source to help investigate these regions, because their emission wave length as well gain spectrum can be engineered through artificial design \cite{gmachl2002ultra}. To date, only n-type QCLs are successfully realized lasing.  One of the most commonly used material combination for active region is GaAs (well) and $Al_{x}Ga_{1-x}As$ (barrier), where x is the relative amount ration of aluminum to gallium. The intersubband transmission occurs in conduction band, as Fig. shows. Add--> one module of repeated QCL heterostructures!

As a novel type of laser as well as efficient source to generate tera Herz (THz) radiation, THz QCLs showed great potential and have attracted already a lot attentions for developing their possible applications. Compared to X-ray, THz radiation owns relative lower energy ($E=h\nu$), which iwouldn't lead to ionising but still can penetrate many materials (e.g. clothes, paper) except for metals \cite{williams2007terahertz}.  Therefore, it could be used as imaging and sensing for security detection in airport \cite{federici2005thz}, which wouldn't affect the health of our bodies. Another interesting area is astronomy, such as heterodyne receivers \cite{williams2007terahertz}, which requires THz QCLs. Because the radiation from universe is mainly with THz, the research of THz technologies would help to detect and observe those unnoticed radiation from galaxies.

@@

Although there are already those successful experimental attempts by active mode-locking, but a complete theory system is still not available. Different with experimental attempts, theoretical modeling requires more understanding of physical effects and accurate mathematical description as well as assumptions. Due to limited knowledge of unfavorable physical effects and lack of consolidation theory about its mechanism, it has been proven to be difficult to directly employ existing techniques from the ultra fast optics community to realize mode-locking of QCLs, active mode-locking is regarded as a efficient way to achieve it. However, both modulation power and frequency need to be set adequate to get mode-locking.

Currently, all those simulation methods are based on optical modeling, in which assuming that the applied electrical voltage signal on cavity is constant. But in fact it's not realistic, this electric signal also has wave nature and will propagate along cavity in the same direction as optical field propagation due to the microstrip transmission line structure of QCLs.
\section{Related work}
Accompanied with experimental research, modeling techniques for QCLs are also steady investigated to help get a deep understanding of internal mechanisms and explore unknown effects. Thanks for persistent efforts of researchers, there are already several models as well as solvers which could be used for describing and analyzing various of processes in QCLs, such as density matrix approach \cite{weber2009density}, Maxwell-Bloch equations \cite{gordon2008multimode}, non-equilibrium Green’s function theory \cite{kubis2008non} along with some other modified methods aimed to take more linearities and effects into account. These models have been used, for example, to investigate modulation properties of optical injection-locked QCLs \cite{wang2013rate}, to calculaton for four-level scheme THz QCLs \cite{yasuda2009nonequilibrium}.

@@

\section{Objective}
The objectives of this thesis are as follows:
\begin{enumerate}
\item To build a dynamic model with coupled Maxwell-Bloch equations and  Transmission line method;
\item To verify "pulling effect" in active mode-locking by simulation;
\item To acquire optimal simulation parameters to generate short pulse;
\item To gain a deep understanding of mode-locking behaviors to help QCLs design in the future.
\end{enumerate}

\chapter{Theory}
QCL is composed of a great amount of repeated stacks of heterojunctions, its extreme thin layers (in the order of a few nanometers) of different materials result in the formation of quantum wells and barriers. By solving steady Schroedinger-Poisson equation system, eigenenergies and wave functions of eigenenergies can be determined, which help to design and optimization of QCL structures (e.g. radiation frequency, injection efficiency). Transfer matrix method \cite{jonsson1990solving} and finite-difference method \cite{tan1990self} are efficient methods to help compute numerical solutions of these systems. 
\section{Maxwell-Bloch equations}
As a semi-classical approach, Maxwell-Bloch equations are widely to describe carrier dynamics as well as field dynamics in a laser. Bloch equations are similar with rate equations, but instead of considering scattering rate of laser levels, they model interaction of electrons on different energy levels by using density matrix. For example, a 3-level system is illustrate in Fig. \ref{fig:MB_levelsystem}. As the active region of QCLs consists of periodic structures, for a single period, Bloch equations can be closed by assuming periodic boundary condition $J_{in}=J_{out}$, where J is injection current density.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/MB_levelsystem}
\caption{: Carrier transition in an injector/3-level/extractor system. |ULL> denotes upper laser level and |LLL> is lower laser level. Injector and extractor stand for laser levels in injections region.}
\label{fig:MB_levelsystem}
\end{center}
\end{figure}

Bloch equations are complemented by Maxwell equation or wave equation to include dynamics of electric field (in the direction of propagation). 
\section{Transmission line}
Transmission line model was created by Oliver Heaviside \cite{heaviside2008electromagnetic} and usually consists of two separated conductors and medium in between (Fig. \ref{fig:TLcircuit}). The conventional TLM is based on Telegrapher's equations (\ref{eq:TLequation1})(\ref{eq:TLequation2}), which describe the evolution of voltage and current both spacial and temporal on an electrical transmission line. These two differential equations contains four distributed components (R', L', G', C') which vary from different transmission lines: R' is distributed resistance of conductors, which is represented by a series resistor in ohms per unit length ($\Omega /m$); L' is distributed inductance resulting from the magnetic field around the line due to self-inductance, which is represented by a series inductor in henries per unit length ($H/m$); G' is distributed conductance of the dielectric material separating the two conductors, which is expressed in siemens per unit length ($S/m$) and represented by a shunt resistor with resistance of 1/G'; C' is distributed capacitance of transmission line, which is represented by a shunt conductor in farads per unit length ($F/m$).
% TL equivalent circuit figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{images/TLcircuit}
\caption{: Schematic representation of the elementary component of a transmission line. $Z_{in}$ denotes wire impedance.}
\label{fig:TLcircuit}
\end{center}
\end{figure}

Transmission line can be further classified in lossy/non-lossy transmission line and uniform/nonuniform transmission line with regarding to characteristics of its conductors and medium. When no resistance (conductor) and conductance (dielectric medium) exist, it can be regarded as ideal transmission line which contains only L' and G'. In uniform transmission line all those distributed components are uniformly distributed along line. Therefore, under the assumptions above and considering the conductance of active region, the simulated QCL can be defined as a one-dimensional (1D) nonlinear non-uniform lossy transmission line, which is more complex than common transmission line problems.

% Transmission line equations
Telegrapher's equations:
\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation1}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-G'v(x,t) \label{eq:TLequation2}
\end{eqnarray}

\section{Mode-locking}
Light generated by lasers owns high coherent compared with from other light sources. Nevertheless, it has still large bandwidth of optical gain, the modes inside cavity osculate independently and don't have fix phase, which leads to wide pulse. By uncertainty principle, if pulse duration is quite short, its bandwidth muss be larger. For example, for a Gaussian shape pulse the minimum possible pulse duration $\Delta t$ can be calculated with
\begin{equation}
\Delta t=\frac{0.441}{N\Delta \nu}.
\end{equation}
Where 0.441 is pulse shape dependent time bandwidth product, which for a hyperbolic-secant-squared pulse shape is 0.315. N and $\Delta \nu$ is amount of modes and bandwidth of pulse, respectively. This formula above could be be used for roughly evaluating the shortest possible pulse width. However, in real case, many other factors have to be taken into consideration, such as dispersion of the cavity, pulse shape and so on.

@@

For active mode-locking, ideally the modulation frequency is exactly at $ f_{tr}$, but even if modulated at frequency of a little variation with $ f_{tr}$, the laser could still be mode-locked, the maximal possible frequency interval is called locking range.
\chapter{Model}
The dynamic model consists of two parts. One of them is optical modeling, which is used for describing the carrier transition  as well as light propagation inside cavity (microcosmic). The other is based on transmission line to obtain voltage and current distribution along cavity (microcosmic). Although each of them has separate solver, both will be simulated simultaneously and can affect with each other.
\section{Optical modeling}
Similar with the existing modeling methods, in this model light propagation is described with Maxwell' equation while carrier transition is determined by Bloch equation. Without regard to lateral non-uniform distribution at boundaries \cite{huang2014non, dhar2015nanoscopic} QCL can be simplified to 1D structure in the direction of propagation (x axis), which means the electrical components were uniformly distributed throughout the cross-sectional area.

\subsection{Carrier transition}
To simulate active region of QCLs, the density matrix model from Ref. [cite Belyanin] was applied to include total of four subband levels, and more importantly to allow all relevant system parameters, such as the eigenenergies, dipole moments and all scattering rates to be bias dependent.

As a prototypical QCL design, the sub-band structure configuration illustrated in Fig. \ref{fig:4Levels}, consists of 4 relevant levels per period, i.e. levels from 1 to 4, where level 4 denotes the upper laser state, level 3 the lower laser level, level 2 is an extraction level which eases the electron extraction from 3, and finally level 1 denotes the depopulation level of the period, which also coincides with the injector state (1') of the next module.

@@

The time evolution of the density matrix is given by the von Neumann equation, which was coupled with a wave equation. $E_z(x,t)$ denotes the $z$-component of electric field (and also the assumed laser growth direction).  
\begin{subequations}
	\label{eq:dmequations}
 \begin{align}
	\frac{d\rho_{44}}{dt} &= J +i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 4} \frac{\rho_{jj}}{\tau_{j\rightarrow 4}}  - \frac{\rho_{44}}{\tau_{4}}, \\
	\frac{d\rho_{33}}{dt} &= -i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 3} \frac{\rho_{jj}}{\tau_{j\rightarrow 3}} - \frac{\rho_{33}}{\tau_{3}}, \\
	\frac{d\rho_{22}}{dt} &= \sum_{j\neq 2} \frac{\rho_{jj}}{\tau_{j\rightarrow 2}} - \frac{\rho_{22}}{\tau_{2}}, \\
	\frac{d\rho_{11}}{dt} &=  -J + \sum_{j\neq 1} \frac{\rho_{jj}}{\tau_{j\rightarrow 1}} - \frac{\rho_{11}}{\tau_{1}}, \\
	\frac{d\rho_{43}}{dt} &= - i\omega_{43}\rho_{43} + i\frac{ez_{43}}{\hbar}E_z(\rho_{44}-\rho_{33})-\Gamma_{\parallel 43}\rho_{43}.
 \end{align}
\end{subequations}
In Eqs. (\ref{eq:dmequations}) $\rho_{ij}$ denotes the $ij-$th density matrix element,  $z_{43}$ the optical transition's dipole moment, $e$ the elementary charge, $\hbar$ is the reduced Plank's constant. Also the parameter $1/\tau_{i\rightarrow j}$ is the net scattering rate from level $i$ to level $j$, calculated by our ensemble Monte Carlo code and incorporating, amongst others, longitudinal optical (LO) phonon, interface roughness and electron electron scattering mechanisms [cite]. Lastly $1/\tau_{i} = \sum_j 1/\tau_{i\rightarrow j}$ is the inverse lifetime of level $i$ and $\Gamma_{\parallel 43} = (\tau_4+\tau_3)/(2\tau_4\tau_3)+1/\tau^*$ is the dephasing rate of the optical transition, including lifetime broadening and a phenomenological pure dephasing $1/\tau^*$ rate due to intrasubband scattering processes [cite ANDO model]. The only scattering mechanism treated quantum mechanically is the optical transition between the upper and lower laser states. One can also fully coherently include resonant tunneling between the injector 1' and the upper laser state 4, which leads to a modified system of equations with larger number of independent variables and is thus more computationally demanding [cite]. Furthermore such an approach does not allow for the inclusion (without $k-$space discretization) of second order tunneling current into the simulations, which has been shown to be the origin of negative the differential conductivity and dispersive gain in quantum cascade lasers [].

@@

\subsection{Light propagation}
The wave equation inside cavity can be described by the following equation with assumption of weak nonlinearity and inhomogeneity
\begin{align}
\label{eq:waveqn}
\left [\frac{c^2}{n_{THz}^2} \frac{\p^2}{\p x^2} -\frac{\p^2}{\p t^2} \right ] E_z =\frac{1}{\epsilon_0 n_{THz}^2}\frac{\p^2}{\p t^2}P,
\end{align}
where  $n_{THz}$ denotes the background refractive index of the bulk active region, $c$ is the velocity of light in vacuum and $\epsilon_0$ is the permittivity of free space. The symbol $P$ denotes the (nonlinear) polarization of the two level system and is given by 
\begin{equation}
P(x,t) =  -\frac{n^s}{L_p}\Gamma ez_{43} (\rho_{43}+\rho_{34}),  
\end{equation}
with $\Gamma$ is the field confinement factor and $L_p$ is the period length.

For the final set of equations, the rotating wave and slowly varying envelope approximations [cite] are employed in order to reduce the wave equation (\ref{eq:waveqn}) to a pair of propagation equations, an fast oscillating terms from the density matrix equations (\ref{eq:dmequations}) was eliminated as well. The corresponding final formulas are slightly modified versions of those in [cite me, cite belyanin], and therefore we omit them here for brevity. Besides, in all subsequent calculations, the effect of the inversion grating on to the current density has been taken into consideration, in an analogous manner to [cite belyanin].

@@

\begin{eqnarray}
\frac { \partial V(x,t) }{ \partial x }  &=& -L'\frac { \partial I(x,t) }{ \partial t }-R'\tilde i(x,t) \label{eq:TLequation5}\\
\frac { \partial I(x,t) }{ \partial x }  &=& - C'\frac { \partial V(x,t) }{ \partial t }-wJ(x,t). \label{eq:TLequation6}
\end{eqnarray}
where V(x,t) and I(x,t) are voltage and current signal at a node x. 
\subsubsection{Boundary conditions}
Boundary conditions account for the completeness of differential equations at the boundary. In order to refine the boudaries and avoid hard variation of electrical components, a cascading of $\pi$ networks\cite{orlandi1996fdtd} is introduced for the distributed transmission line by splitting the shunt capacitance and conductance in half with two parallel capacitors and conductors at boundary, which is illustrate in Fig. \ref{fig:BoundaryCondition}.

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltaged can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. Due to existence of wire impedance there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/pi_representation.pdf}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit. }
\label{fig:BoundaryCondition}
\end{center}
\end{figure}
